### 2019-10-31 monograph/chapters/introduction.tex
Added missing Dr. to the advisor name on main.tex
Created the motivation chapter on introduction.tex

    Então,
    quando diferentes programadores cooperam em grandes projetos,
    \advisor{como unir pessoas com experiências e
        preferências diferentes?%
    }{%
    como essas pessoas todas poderiam trabalhar juntas,
    mesmo elas não tendo as mesmas experiências?} \advisor{Uma}{Assim,
    uma} barreira adicional \advisor{ao}{para cada um desses programadores no} desenvolvimento do projeto será aprender as diferenças de trabalho que cada um desses desenvolvedores possuem entre si.

@@

@@

\advisor{%
    Esta seção apresenta os objetivos desse trabalho,
    divididos em Objetivo Geral e
    Objetivos Específicos.
}{%
    \lang{%
        Beforehand due the scope limitation for a Graduation Thesis,
        we should only think about a basic, simple,
        and yet reusable core of features.
    }{%
        Devido ao trabalho tratar~=se de uma tese de graduação,
        limita~=se seu escopo de trabalho a criação de um núcleo básico de recursos.
    }%
    \lang{%
    \begin{enumerate}
        \item
            A Software Product with a great Object Orientation and
            possibilities of extension of features,
            decent research on the state of the art.
        \item
            Ranking all code formatting classes (beautifying) applicable.
            Including a study on what does is source beautifying,
            how to do such and
            why.
        \item
            Establish relationships between good programming practices and
            efficiency in programming,
            in addition to a new tool to support programmers in order to automate the long and
            diverse programming process in teams of developers with different programming `best practices'.
        \item
            Define,
            determine and
            classify which one are good programming practices and
            perform an in\hyp{}depth study on the good practices on visual layout area,
            also known as code `Beautifying'.
        \item
            The definition of a flow pattern of development allowing teams of developers with different programming best practices,
            to work without intervene with each other up to start wars of `best good practices'.
        \item
            Discourse on the variety of existing tools for the support of good programming practices,
            with a comparative analysis between them,
            determining their weaknesses and
            strengths.
    \end{enumerate}
    }{%
        Enumerar e
        explicar as ferramentas de formatação de código~=fonte e
        realizar o desenvolvimento de uma nova ferramenta de formatação de código~=fonte que seja extensível por gramáticas fornecidas pelos usuários.
    }
}%

>>>>

    Quando diferentes programadores cooperam em grandes projetos,
    \advisor{como unir pessoas com experiências e
        preferências diferentes?%
    }{%
    como essas pessoas todas poderiam trabalhar juntas,
    mesmo elas não tendo as mesmas experiências?} \advisor{Uma}{Assim,
    uma} barreira adicional \advisor{ao}{para cada um desses programadores no} desenvolvimento do projeto será aprender as diferenças de trabalho que cada um desses desenvolvedores possuem entre si.

@@

\section{Motivação}

Ter que aprender e
configurar muitas ferramentas de formatação de código~=fonte é um tarefa cansativa e
exaustante (\fullref{formatadores_de_codigo}).
Mais ainda,
escrever uma nova ferramenta de formatação de código~=fonte para cada nova linguagem de programação que surgir.
Mesmo que estes pontos não fossem problema,
cada ferramenta de formatação de código~=fonte possui diferentes níveis de profundidade e
detalhamento no qual elas se integram com a (ou as) linguagens de programação que elas suportam.
O que pode tornar frustrante migrar de uma linguagem de programação para outra,
pela perda de controle da ferramenta de código~=fonte.

@@

\advisor{%
    Esta seção apresenta sucintamente os objetivos desse trabalho,
    divididos em Objetivo Geral e
    Objetivos Específicos.
}{%
    \lang{%
        Beforehand due the scope limitation for a Graduation Thesis,
        we should only think about a basic, simple,
        and yet reusable core of features.
    }{%
        Devido ao trabalho tratar~=se de uma tese de graduação,
        limita~=se seu escopo de trabalho a criação de um núcleo básico de recursos.
    }%
    \lang{%
    \begin{enumerate}
        \item
            A Software Product with a great Object Orientation and
            possibilities of extension of features,
            decent research on the state of the art.
        \item
            Ranking all code formatting classes (beautifying) applicable.
            Including a study on what does is source beautifying,
            how to do such and
            why.
        \item
            Establish relationships between good programming practices and
            efficiency in programming,
            in addition to a new tool to support programmers in order to automate the long and
            diverse programming process in teams of developers with different programming `best practices'.
        \item
            Define,
            determine and
            classify which one are good programming practices and
            perform an in\hyp{}depth study on the good practices on visual layout area,
            also known as code `Beautifying'.
        \item
            The definition of a flow pattern of development allowing teams of developers with different programming best practices,
            to work without intervene with each other up to start wars of `best good practices'.
        \item
            Discourse on the variety of existing tools for the support of good programming practices,
            with a comparative analysis between them,
            determining their weaknesses and
            strengths.
    \end{enumerate}
    }{%
        Enumerar e
        explicar as ferramentas de formatação de código~=fonte e
        realizar o desenvolvimento de uma nova ferramenta de formatação de código~=fonte que seja extensível por gramáticas fornecidas pelos usuários.
    }
}%
